Sampling requirements to detect ecosystem change

### 2020-03-16 R/manuscript_draft.Rmd
comments post Skype meeting

Authors: Rosalie Bruel$^{1}$ and Easton R. White$^{2}$

@@

Addresses: $^{1}$Rubenstein Ecosystem Science Laboratory, University of Vermont, VT 05405, USA, https://orcid.org/0000-0001-8351-7539 $^{2}$Department of Biology, University of Vermont, VT 05405, USA, https://orcid.org/0000-0002-0768-9555

@@

- theoretical results
- example with the case study
- how this fits in with other work
- limitations and future work

>>>>

Authors: Rosalie Bruel$^{1*}$ and Easton R. White$^{2*}$

@@

Addresses: $^{1}$Rubenstein Ecosystem Science Laboratory, University of Vermont, VT 05405, USA, https://orcid.org/0000-0001-8351-7539 $^{2}$Department of Biology, University of Vermont, VT 05405, USA, https://orcid.org/0000-0002-0768-9555
* Both authors contributed contributed equally and order was chosen alphabetically / by latitudinal gradient of birth place

@@

- reexplain and compare the 3 methods (theoretical (Fig 3) vs case study (Fig 4), and how they relate (Fig 2))
- money implications (before or now)  
- how this fits in with other work: examples of situation it would be applied (Rosalie)  
- how this doesn't fit with other work (limitations) (Rosalie)
- future work  (?)
